Research Notes

### 2018-11-18 writeups/notes.tex
Stash

>>>>

\chapter{State of the Art}

While the succeeding content is largely chronological, this chapter will be
devoted to a description of the current state-of-the-art.

\section{2D Cartesian, Pseudo-Anelastic Atmosphere}

Our equations are:
\begin{subequations}\label{se:base.pseudo-anel}
    \begin{align}
        \vec{\nabla} \cdot \vec{u} &= 0,\\
        \pd{\rho_1}{t} - \frac{u_{1z} \rho_0}{H}
            + \vec{u} \cdot \vec{\nabla}\rho_1 &= 0,\\
        \pd{\vec{u}_1}{t} + \p*{\vec{u} \cdot \vec{\nabla}}\vec{u}_1
            + \frac{\vec{\nabla}P_1}{\rho_0} + \frac{\rho_1 \vec{g}}{\rho_0}
            - \frac{\vec{\nabla}P_1}{\rho_0}\rho_1 &= 0.
    \end{align}
\end{subequations}
Note that we permit background stratification $-\pd{\ln \rho_0}{z} = H$ but no
background shear flow $\vec{u}_0$, so we write $\vec{u}_1 = \vec{u}$ without
ambiguity.

\section{2D Cartesian, Boussinesq Local Simulations}

Our equations are the same:
\begin{subequations}\label{se:base.bouss}
    \begin{align}
        \vec{\nabla} \cdot \vec{u} &= 0,\\
        \pd{\rho_1}{t} - \frac{u_{1z} \rho_0}{H}
            + \vec{u} \cdot \vec{\nabla}\rho_1 &= 0,\\
        \pd{\vec{u}_1}{t} + \p*{\vec{u} \cdot \vec{\nabla}}\vec{u}_1
            + \frac{\vec{\nabla}P_1}{\rho_0} + \frac{\rho_1 \vec{g}}{\rho_0}
            - \frac{\vec{\nabla}P_1}{\rho_0}\rho_1 &= 0.
    \end{align}
\end{subequations}
The only difference is that we take $\rho_0(z) = \rho_0$, effectively assuming
$H$ is much larger than the vertical extent of the domain of simulation.
